Transcriptional dynamics of influenza virus infection in single cells

### 2017-09-09 paper/paper.tex
Additional paragraph devoted to diversity in discussion, final paragraph edited slightly

@@

The success garnered here underscores that single-cell approaches seem distinctly suited to study of viral pathogens, as not only are many host responses governed by bimodality and stochasticity ~\citep{Shalek:2014ey,Shalek:2013ej}, but also viral populations themselves exhibit a staggering array of diversity.
Our results with influenza have provided significant support for earlier analysis of viral stochasticity, further defined the sources and impacts of that stochasticity, and generated potentially fertile avenues of research. 
While it is early days yet, it is our hope that our efforts will contribute to a deeper understanding of viral populations, treating population-level measurements as emergent phenomena defined by underlying individual stochasticity rather than analyzing viral replication in a strictly deterministic framework.

>>>>

It is immediately apparent that a model of influenza infection wherein there is equivalent accumulation of transcripts across successfully infected cells is far to facile to describe the true situation.
While infection certainly proceeds over time, with gradual increase in influenza transcript abundance, the level of transcripts expressed in cells varies wildly.
While some of these differences are likely due to temporal variation in binding and internalization, it will be interesting in follow-up experiments to determine whether there is an ultimate level of influenza transcript that is invariably reached or whether the variation we observe is indicative of a final setpoint.
Indeed, our analyses of host transcriptomes suggests that those cells expressing higher levels of influenza are distinguishable, even at 6 hours, from later time points expressing similar influenza burden, giving an indication that there are features above-and-beyond temporal variation driving differences in viral mRNA expression\jdbcomment{If we make this point we need to add the ranked graph to the results and address it} .

@@

The success garnered here underscores that single-cell approaches seem distinctly suited to study of viral pathogens, as not only are many host responses governed by bimodality and stochasticity ~\citep{Shalek:2014ey,Shalek:2013ej}, but also viral populations themselves exhibit a staggering array of diversity.
Our results with influenza have provided significant support for earlier analysis of viral stochasticity, further defined the sources and impacts of that stochasticity, and generated potentially fertile avenues of research. 
We stand now at an exciting moment in virology, as technology allows us to observe population-level measurements as emergent phenomena defined by underlying individual stochasticity rather than analyzing viral replication in a strictly deterministic framework.
It is our hope that this work will serve not only as a window into influenza replication, but as a part of a grander design in re-examining and understanding the fundamental features of viral infection.
